Lasso_RCI_Response

### 2024-05-21 Lasso_RCI_Response.Rmd
Mindfulness variables

AAQIIpre <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
AAQIIpre <- AAQIIpre |>
  mutate(
    AAQIIpre = AAQIIpre_1_1 + AAQIIpre_2_1 + AAQIIpre_3_1 + AAQIIpre_4_1 + 
      AAQIIpre_5_1 + AAQIIpre_6_1 + AAQIIpre_7_1
  )
Mothership <- left_join(Mothership,AAQIIpre, by = join_by(ID1 == ID1))
AAQII

@@

view(Mothership)
# df_5 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_4250-4350.sav")
```

@@

# only include people that attend treatment & its thier first time attending
Mothership <- Mothership |>
  filter(
    is.na(Prev_AdmitID_1),
    C_Admit_1 == 1
  ) |>
  mutate(
    dummy = -99
  ) |>
  filter(!is.na(Disorder_treat),
         !is.na(TxYear),
         !is.na(Duration))

@@

#4 Adding it back to mother ship
    Mothership_post <- Mothership_post |>
      mutate(
        CUDOS_first = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
        CUDOS_first = ifelse(CUDOS_first < 0, NA, CUDOS_first),
        CUXOS_first = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
        CUXOS_first = ifelse(CUXOS_first < 0, NA, CUXOS_first),
        CUDOS_pre = BL_CUDOS,
        CUXOS_pre = BL_CUXOS,
        CUDOS_post = ifelse(!is.na(SUMdep_DC), SUMdep_DC,Post_Dep),
        CUDOS_post = ifelse(CUDOS_post < 0, NA, CUDOS_post),
        CUXOS_post = ifelse(!is.na(SUManx_DC), SUManx_DC,Post_anx),
        CUXOS_post = ifelse(CUXOS_post < 0, NA, CUXOS_post),
#5 Making some other varaibles
        BL_Missing = as.factor(ifelse(is.na(BL_CUXOS), "Anx Missing",
                                      ifelse(is.na(BL_CUDOS), "Dep Missing", "Not Missing"
                                      ))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUXOS),NA,
                                                       ifelse(is.na(BL_CUDOS),NA, "Sub Both"
                                                       )))))),
        Sig_BL_Anx = as.factor(ifelse(BL_CUXOS > 20, "Significant",
                                      ifelse(is.na(BL_CUXOS),NA, "Subclinical"
                                      ))),
        Sig_BL_Dep = as.factor(ifelse(BL_CUDOS > 20, "Significant",
                                      ifelse(is.na(BL_CUDOS),NA, "Subclinical"
                                      ))),
        Sig_Post_Anx = as.factor(ifelse(CUXOS_post > 20, "Significant",
                                        ifelse(is.na(CUXOS_post),NA, "Subclinical"
                                        ))),
        Sig_Post_Dep = as.factor(ifelse(CUDOS_post > 20, "Significant",
                                        ifelse(is.na(CUDOS_post),NA, "Subclinical"
                                        ))),
        Any_Sig_BL = as.factor(ifelse(BL_CUXOS > 20 | BL_CUDOS > 20, "Sig",
                                      ifelse(is.na(BL_CUXOS),NA,
                                             ifelse(is.na(BL_CUDOS),NA, "Sub"
                                             )))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUDOS), NA,
                                                       ifelse(is.na(BL_CUXOS), NA, "Subclinical"
                                                       ))))))
)

# 4. RCI Analysis categorization ------------------------------------------

@@

library(JTRCI)
citation("JTRCI")

# 
# #devtools::install_github("zieglema/ClinicalSig")
#1. Create df for RCI
RCI_df_dep <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

RCI_df_anx <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

RCI_df_dep <- data.frame(RCI_df_dep)
RCI_df_anx <- data.frame(RCI_df_anx)

# https://awkruijt.netlify.app/plotposts/longitudinaljtrci

RCI_df_anx1<-RCI_df_anx |>
  select(ID1,pre,post)

## Using RCI only (respond/nonrespond/deteriorated)
DEP_RCI <- JTRCI (data = RCI_df_dep, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  JTcrit = "auto",
                  plottitle = "JT indices for anxiety")

ANX_RCI <- JTRCI (data = RCI_df_anx, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  #JTcrit = "auto",
                  plottitle = "JT indices for depression")
RCI_DF<- ANX_RCI$data
colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")

RCI_DF2<- DEP_RCI$data
colnames(RCI_DF2) <- paste0(colnames(RCI_DF2),"_dep")

RCI_DF <- full_join(RCI_DF,RCI_DF2, by = c("ppid_anx" = "ppid_dep"))
colnames(RCI_DF)[1] = "ID1"

head(RCI_DF)
```

```{r}
view(Mothership_post)
```

```{r}
#Using JT citeria (recovered/improved/nonresponse/deteriorated)

#1. JT classification for depression
JTRCI (data = RCI_df_dep, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "JT", 
                  JTcrit = "auto",
                  plottitle = "JT indices for anxiety")

DEP_JT <- JTRCIdf
colnames(DEP_JT) <- paste0(colnames(DEP_JT),"_dep")
head(DEP_JT)

#2. JT classification for anxiety
JTRCI (data = RCI_df_anx, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "JT", 
                  #JTcrit = "auto",
                  plottitle = "JT indices for depression")

ANX_JT<- JTRCIdf

#3. Make combined JT table for anxiety and depression

# JT_DF<- ANX_JT

colnames(ANX_JT) <- paste0(colnames(ANX_JT),"_anx")

# 
# JT_DF2<- DEP_JT

# 
# JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
# colnames(JT_DF)[1] = "ID1"

head(ANX_JT)
```

@@

Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
    #ACT stuff
    AAQIIpre, AAQIIpost, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post, FFMQ_post_total, 
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre, FFMQ_post_total
  ))
Mothership_lasso_1 <- na.omit(Mothership_lasso)

@@

RCI_df_anx2 <- Mothership_lasso_1 |>
  filter(
    !is.na(CUXOS_pre),
    !is.na(CUXOS_post),
    CUXOS_pre > 20,
  )|>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

colnames(ANX_JT_smol) <- paste0(colnames(ANX_JT_smol),"_anx")

view(ANX_JT_smol)
view(DEP_JT_smol)
```

@@

Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have data
  filter(!is.na(Days_complete_1)) |>
  #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100
  )
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    # Anx_Responder = as.factor(
    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  <= -50, "Responder",
    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
    #   )),
    # Dep_Responder = as.factor(
    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange <= -50, "Responder",
    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
    #   )),
    # Treatment_Responder = as.factor(
    #   ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
    #   ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      # )))))))))))

@@

# Data analysis 
## Part 1: Methods information
```{r}
summary(as.factor(Mothership_post_joined$SCID_1))
```

@@

```{r}
### Anxeity 
Mothership_lasso_anx <- Mothership_post_anx |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  !is.na(Anxiety_Responder),
  CUXOS_pre >= 20,
  ) |>
  select( c(
    ID1,Anxiety_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
        #ACT stuff
    AAQIIpre, AAQIIpost, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post, FFMQ_post_total, 
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre, FFMQ_post_total
  ))
Mothership_lasso_anx <- na.omit(Mothership_lasso_anx)

### depression
Mothership_lasso_dep <- Mothership_post_dep |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Depression_Responder),
    CUDOS_pre >= 20,
  ) |>
  select( c(
    ID1, Depression_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
    #ACT stuff
    AAQIIpre, AAQIIpost, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post, FFMQ_post_total, 
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre, FFMQ_post_total

@@

```{r}
# t test scores for differences pre post, between and within groups. 
Pre_Post_t_Scores <- c("")

@@

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, #Psychotic_D,  
    Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
# Pre variables
    CUDOS_pre,CUXOS_pre,
    AAQIIpre,
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
    Acting_mindful_pre,
  #post stuff    
     # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1,
    # RDQ
    # rdqPOST_coping:rdqPOST_wbs,
    #ACT stuff

    AAQIIpost,
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post,

  ))

# old model
# Anxiety_D, Mood_D, BPD_P,    Trauma_D,  Other,
#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
#     Current_Dx,

@@

# Make predictions on the test data
x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
probabilities <- model.min %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Depression_Responder
mean(predicted.classes == observed.classes)

#Using lambda.min as the best lambda, gives the following regression coefficients:
coef(cv.lasso.dep, cv.lasso.dep$lambda.min)

#Using lambda.1se as the best lambda, gives the following regression coefficients:
coef(cv.lasso.dep, cv.lasso.dep$lambda.1se)
```

>>>>

AAQIIpre <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
AAQIIpre <- AAQIIpre |>
  mutate(
    AAQIIpre = AAQIIpre_1_1 + AAQIIpre_2_1 + AAQIIpre_3_1 + AAQIIpre_4_1 + 
      AAQIIpre_5_1 + AAQIIpre_6_1 + AAQIIpre_7_1
  )
Mothership <- left_join(Mothership,AAQIIpre, by = join_by(ID1 == ID1))

@@

# df_5 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_4250-4350.sav")
```

@@

# only include people that attend treatment & its thier first time attending
Mothership <- Mothership |>
  filter(
    is.na(Prev_AdmitID_1),
    C_Admit_1 == 1
  ) |>
  mutate(
    dummy = -99
  )
  # filter(!is.na(Disorder_treat),
  #        !is.na(TxYear),
  #        !is.na(Duration))

@@

#4 Adding it back to mother ship
    Mothership_post <- Mothership_post |>
      mutate(
        CUDOS_first = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
        CUDOS_first = ifelse(CUDOS_first < 0, NA, CUDOS_first),
        CUXOS_first = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
        CUXOS_first = ifelse(CUXOS_first < 0, NA, CUXOS_first),
        CUDOS_pre = BL_CUDOS,
        CUXOS_pre = BL_CUXOS,
        CUDOS_post = ifelse(!is.na(SUMdep_DC), SUMdep_DC,Post_Dep),
        CUDOS_post = ifelse(CUDOS_post < 0, NA, CUDOS_post),
        CUXOS_post = ifelse(!is.na(SUManx_DC), SUManx_DC,Post_anx),
        CUXOS_post = ifelse(CUXOS_post < 0, NA, CUXOS_post),
#5 Making some other varaibles
        BL_Missing = as.factor(ifelse(is.na(BL_CUXOS), "Anx Missing",
                                      ifelse(is.na(BL_CUDOS), "Dep Missing", "Not Missing"
                                      ))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUXOS),NA,
                                                       ifelse(is.na(BL_CUDOS),NA, "Sub Both"
                                                       )))))),
        Sig_BL_Anx = as.factor(ifelse(BL_CUXOS > 20, "Significant",
                                      ifelse(is.na(BL_CUXOS),NA, "Subclinical"
                                      ))),
        Sig_BL_Dep = as.factor(ifelse(BL_CUDOS > 20, "Significant",
                                      ifelse(is.na(BL_CUDOS),NA, "Subclinical"
                                      ))),
        Sig_Post_Anx = as.factor(ifelse(CUXOS_post > 20, "Significant",
                                        ifelse(is.na(CUXOS_post),NA, "Subclinical"
                                        ))),
        Sig_Post_Dep = as.factor(ifelse(CUDOS_post > 20, "Significant",
                                        ifelse(is.na(CUDOS_post),NA, "Subclinical"
                                        ))),
        Any_Sig_BL = as.factor(ifelse(BL_CUXOS > 20 | BL_CUDOS > 20, "Sig",
                                      ifelse(is.na(BL_CUXOS),NA,
                                             ifelse(is.na(BL_CUDOS),NA, "Sub"
                                             )))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUDOS), NA,
                                                       ifelse(is.na(BL_CUXOS), NA, "Subclinical"
                                                       ))))))
)
```

```{r}
# 4. RCI Analysis categorization ------------------------------------------

@@

library(JTRCI)

# # 
# # #devtools::install_github("zieglema/ClinicalSig")
# #1. Create df for RCI
# RCI_df_dep <- Mothership_post |>
#   mutate(
#     ID1  = as.integer(ID1),
#     pre  = as.numeric(CUDOS_pre),
#     post = as.numeric(CUDOS_post),
#   ) |>
#   select(
#     ID1,pre,post
#   ) |>
#   filter(!is.na(pre),
#          !is.na(post),
#          pre > 20)
# 
# RCI_df_anx <- Mothership_post |>
#   mutate(
#     ID1  = as.integer(ID1),
#     pre  = as.numeric(CUXOS_pre),
#     post = as.numeric(CUXOS_post),
#   ) |>
#   select(
#     ID1,pre,post
#   ) |>
#   filter(!is.na(pre),
#          !is.na(post),
#          pre > 20)
# 
# 
# RCI_df_dep <- data.frame(RCI_df_dep)
# RCI_df_anx <- data.frame(RCI_df_anx)
# 
# # https://awkruijt.netlify.app/plotposts/longitudinaljtrci
# 
# RCI_df_anx1<-RCI_df_anx |>
#   select(ID1,pre,post)
# 
# ## Using RCI only (respond/nonrespond/deteriorated)
# DEP_RCI <- JTRCI (data = RCI_df_dep, 
#                   pre = "pre", 
#                   post = "post", 
#                   ppid = "ID1", 
#                   reliability = .74, 
#                   indextype = "RCI", 
#                   JTcrit = "auto",
#                   plottitle = "JT indices for anxiety")
# 
# ANX_RCI <- JTRCI (data = RCI_df_anx, 
#                   pre = "pre", 
#                   post = "post", 
#                   ppid = "ID1", 
#                   reliability = .74, 
#                   indextype = "RCI", 
#                   #JTcrit = "auto",
#                   plottitle = "JT indices for depression")
# RCI_DF<- ANX_RCI$data
# colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")
# 
# RCI_DF2<- DEP_RCI$data
# colnames(RCI_DF2) <- paste0(colnames(RCI_DF2),"_dep")
# 
# RCI_DF <- full_join(RCI_DF,RCI_DF2, by = c("ppid_anx" = "ppid_dep"))
# colnames(RCI_DF)[1] = "ID1"
# 
# head(RCI_DF)
```

```{r}
#Using JT citeria (recovered/improved/nonresponse/deteriorated)
# 
# #1. JT classification for depression
# JTRCI (data = RCI_df_dep, 
#                   pre = "pre", 
#                   post = "post", 
#                   ppid = "ID1", 
#                   reliability = .74, 
#                   indextype = "JT", 
#                   JTcrit = "auto",
#                   plottitle = "JT indices for anxiety")
# 
# DEP_JT <- JTRCIdf
# colnames(DEP_JT) <- paste0(colnames(DEP_JT),"_dep")
# head(DEP_JT)
# 
# #2. JT classification for anxiety
# JTRCI (data = RCI_df_anx, 
#                   pre = "pre", 
#                   post = "post", 
#                   ppid = "ID1", 
#                   reliability = .74, 
#                   indextype = "JT", 
#                   #JTcrit = "auto",
#                   plottitle = "JT indices for depression")
# 
# ANX_JT<- JTRCIdf
# 
# #3. Make combined JT table for anxiety and depression
# 
# # JT_DF<- ANX_JT
# 
# colnames(ANX_JT) <- paste0(colnames(ANX_JT),"_anx")
# 
# # 
# # JT_DF2<- DEP_JT
# 
# # 
# # JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
# # colnames(JT_DF)[1] = "ID1"
# 
# head(ANX_JT)
```

@@

Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    # rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
    #ACT stuff
    # AAQIIpre, AAQIIpost,
    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
    # Acting_mindful_pre,
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post,
  ))

Mothership_lasso_1 <- na.omit(Mothership_lasso)

@@

```{r}
RCI_df_anx2 <- Mothership_lasso_1 |>
  filter(
    !is.na(CUXOS_pre),
    !is.na(CUXOS_post),
    CUXOS_pre > 20,
  )|>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

colnames(ANX_JT_smol) <- paste0(colnames(ANX_JT_smol),"_anx")
```

@@

# Mothership_post <- Mothership_post |>
#   #1. Filter out scores for people not in the program / don't have data
#   filter(!is.na(Days_complete_1)) |>
#   #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
#   filter(!is.na(CUXOS_pre),
#          !is.na(CUXOS_post),
#          CUXOS_pre > 0,
#          CUXOS_post >= 0,
#          !is.na(CUDOS_pre),
#          !is.na(CUDOS_post),
#          CUDOS_pre > 0,
#          CUDOS_post>= 0
#          ) |>
#   mutate(
#     Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
#     Delta_Dep_DC = CUDOS_post - CUDOS_pre,
#     Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
#     Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100
#   )
```

```{r}
#Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    # Anx_Responder = as.factor(
    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  <= -50, "Responder",
    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
    #   )),
    # Dep_Responder = as.factor(
    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange <= -50, "Responder",
    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
    #   )),
    # Treatment_Responder = as.factor(
    #   ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
    #   ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      # )))))))))))

@@

# Data analysis 
## Part 1: Methods information
```{r}
# summary(as.factor(Mothership_post_joined$SCID_1))
```

@@

```{r}
### Anxeity 
Mothership_lasso_anx <- Mothership_post_anx |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  !is.na(Anxiety_Responder),
  CUXOS_pre >= 20,
  ) |>
  select( c(
    ID1,Anxiety_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
        #ACT stuff
    AAQIIpre, AAQIIpost, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post, FFMQ_post_total, 
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre, FFMQ_post_total
  ))
Mothership_lasso_anx <- na.omit(Mothership_lasso_anx)

### depression
Mothership_lasso_dep <- Mothership_post_dep |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Depression_Responder),
    CUDOS_pre >= 20,
  ) |>
  select( c(
    ID1, Depression_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
    #ACT stuff
    AAQIIpre, AAQIIpost, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post, 
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre,

@@

T tests
```{r}
# t test scores for differences pre post, between and within groups. 
Pre_Post_t_Scores <- c("")

@@

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    #rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre,CUDOS_pre, 
    #ACT stuff
    # AAQIIpre, AAQIIpost,
    #  Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    # Acting_mindful_pre, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post,
  ))

@@

#####  CHECK THIS OUT?????????

# Make predictions on the test data
x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
probabilities <- model.min %>% predict(newx = x.test,"response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Depression_Responder
mean(predicted.classes == observed.classes)

#Using lambda.min as the best lambda, gives the following regression coefficients:
#coef(cv.lasso.dep, cv.lasso.dep$lambda.min)

#Using lambda.1se as the best lambda, gives the following regression coefficients:
#coef(cv.lasso.dep, cv.lasso.dep$lambda.1se)
```
